---
title: "Depression Trajectories"
author: "Steve Brunwasser"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: 4
    toc_float: yes
    number_sections: yes
    code_folding: hide
    theme: cosmo
    highlight: tango
---
```{r include=FALSE}
knitr::opts_chunk$set( warning = F, message = F )
```


# Workspace prep


Prepare the workspace.
```{r workspace}
load( 'ctsr.use.RData' )

require( Hmisc )
require( rms )
require( lme4 )
require( dagitty )
require( ggeffects )
require( DHARMa )
require( GLMMadaptive )
require( dplyr )
require( table1 )
```

# Descriptive Satistics
```{r }
dd <- datadist( ctsr.use )
options( datadist = 'dd' )

html( describe( ctsr.use ) )
```



```{r}

require( RProbSup )

label( ctsr.use$sex ) <- 'Participant-reported sex'
label( ctsr.use$race2 ) <- 'Participant-reported race'
levels( ctsr.use$race2 ) <- c( 'White/Caucasian','Asian/Asian American','Other race' )
label( ctsr.use$college ) <- 'Parent with a college degree?'
label( ctsr.use$curfinf ) <- 'Current level of financial comfort'
label( ctsr.use$txcur ) <- 'Currently receiving mental health treatment?'
label( ctsr.use$bis ) <- 'BIS/BAS behavioral inhibition composite score'
label( ctsr.use$procrast.t1 ) <- 'Procrastination Scale composite score'
label( ctsr.use$transfer.campus.f ) <- 'Student Type'

ctsr.use.a1 <- subset( ctsr.use, assess == '1'  )

label( ctsr.use.a1$sex ) <- 'Participant-reported sex'
label( ctsr.use.a1$race2 ) <- 'Participant-reported race'
label( ctsr.use.a1$college ) <- 'Parent with a college degree?'
label( ctsr.use.a1$curfinf ) <- 'Current level of financial comfort'
label( ctsr.use.a1$txcur ) <- 'Currently receiving mental health treatment?'
label( ctsr.use.a1$bis ) <- 'BIS/BAS behavioral inhibition composite score'
label( ctsr.use.a1$procrast.t1 ) <- 'Procrastination Scale composite score'
label( ctsr.use.a1$transfer.campus.f ) <- 'Student Type'

( t1 <- table1( ~ sex + race2 + college + curfinf + txcur + bis + procrast.t1 | transfer.campus.f, 
        data = ctsr.use.a1  )
)

```



# Directed Acyclic Graph (DAG)
```{r dag}
dag <- dagitty('dag {
"Adverse life events" [pos="-1.838,-0.653"]
"Current mental health problems" [pos="-0.306,0.955"]
"Finances current" [pos="-1.364,-0.070"]
"Finances past" [pos="0.026,0.057"]
"Parent education" [pos="-0.192,-0.969"]
"Past mental health problems" [pos="0.877,-0.871"]
Depression [outcome,pos="1.182,1.293"]
Genetics [pos="-1.099,-1.831"]
"Student Type" [exposure,pos="-1.798,1.286"]
Inhibition [pos="-1.652,-1.393"]
Procrastination [pos="1.142,-0.289"]
Race [pos="-0.034,-1.885"]
Sex [pos="0.440,-1.721"]
"Adverse life events" -> "Current mental health problems" [pos="-1.301,0.676"]
"Adverse life events" -> "Finances current" [pos="-1.631,-0.413"]
"Adverse life events" -> "Finances past"
"Adverse life events" -> "Past mental health problems"
"Adverse life events" -> Depression
"Adverse life events" -> "Student Type"
"Adverse life events" -> Procrastination
"Current mental health problems" -> Depression
"Current mental health problems" -> "Student Type"
"Current mental health problems" <-> Procrastination
"Finances current" -> "Current mental health problems"
"Finances current" -> Depression
"Finances current" -> "Student Type"
"Finances past" -> "Finances current"
"Finances past" -> "Past mental health problems"
"Parent education" -> "Finances current"
"Parent education" -> "Finances past"
"Parent education" -> Depression
"Past mental health problems" -> "Current mental health problems"
"Past mental health problems" -> Depression [pos="1.014,0.657"]
"Past mental health problems" <-> Procrastination
Genetics -> "Adverse life events"
Genetics -> "Current mental health problems"
Genetics -> "Parent education"
Genetics -> "Past mental health problems"
Genetics -> Depression [pos="-0.253,-0.647"]
Genetics -> "Student Type"
Genetics -> Inhibition
Genetics -> Procrastination
"Student Type" -> Depression
Inhibition -> "Adverse life events"
Inhibition -> "Current mental health problems"
Inhibition -> "Past mental health problems"
Inhibition -> Depression [pos="-0.597,0.257"]
Inhibition -> "Student Type"
Inhibition -> Procrastination [pos="0.096,-0.101"]
Procrastination -> Depression
Procrastination -> "Student Type"
Race -> "Adverse life events"
Race -> "Finances current"
Race -> "Finances past"
Race -> "Parent education"
Race -> Depression
Race -> "Student Type"
Sex -> "Adverse life events"
Sex -> "Current mental health problems" [pos="-0.025,-0.720"]
Sex -> "Past mental health problems"
Sex -> Depression
Sex -> "Student Type" [pos="0.244,-1.199"]
Sex -> Inhibition
}
')

plot( dag )

```

View the DAG's causal implications.
```{r dagimplications}
impliedConditionalIndependencies( dag )
```

View the minimally sufficient adjustment set implied by the DAG.
```{r}
adjustmentSets( dag )
```


# Statistical Modeling

## CTSR

Redundancy analysis to evaluate the extent of multicollinearity 
```{r}

redun( phq ~ transfer.campus.f + txcur + curfin + procrastct + bisct + race2 + male + cohort.f + weeks, data = ctsr.use.a1 )
```


```{r}
html( describe( ctsr.use ) )
```



### m0.symp: Complex poisson model
```{r}
#m0.symp <- mixed_model( fixed = phq ~ transfer.campus.f*rcs( weeks, 3 )
#                 + txcur*rcs(  weeks, 3 )
#                 + rcs( procrastct, 3)*rcs(  weeks, 3 )
#                 + rcs( bisct, 3)*rcs(  weeks, 3 )
#                 + curfin
#                 + race2
#                 + male,
#                 random =~ rcs( weeks, 3 ) | id,
#                 data = ctsr.use,
#                 family = poisson()
#                 )
# 
# save( m0.symp, file = 'm0.symp.Rdata' )
load( 'm0.symp.Rdata' )
```


### m1.symp: Complex negative binomial model

* Adds $df=1$ to *m0.symp* in the form of a $\theta$ parameter to capture overdispersion

```{r}

# m1.symp <- mixed_model( fixed = phq ~ transfer.campus.f*rcs( weeks, 3 )
#                 + txcur*rcs(  weeks, 3 )
#                 + rcs( procrastct, 3)*rcs(  weeks, 3 )
#                 + rcs( bisct, 3)*rcs(  weeks, 3 )
#                 + curfin
#                 + race2
#                 + male,
#                 random =~ rcs( weeks, 3 ) | id,
#                 data = ctsr.use,
#                 family = GLMMadaptive:::negative.binomial()
#                 )
# 
# save( m1.symp, file = 'm1.symp.Rdata' )
load( 'm1.symp.Rdata' )
```


#### COmpare Poisson & negative binomials models
```{r}
( lrt.m0symp.m1symp <- anova( m0.symp, m1.symp ) )
```



### m2.symp: 

* Drop the random coefficients for the nonlinear time 
* Allow random variation around the linear time effect
* 
```{r}

# m2.symp <- mixed_model( fixed = phq ~ transfer.campus.f*rcs( weeks, 3 ) 
#                 + txcur*rcs( weeks, 3 ) 
#                 + rcs( procrastct, 3)*rcs( weeks, 3 )  
#                 + rcs( bisct, 3)*rcs( weeks, 3 ) 
#                 + curfin  
#                 + race2 
#                 + male,
#                 random =~ weeks | id,
#                 data = ctsr.use,
#                 family = GLMMadaptive:::negative.binomial()
#                 )

# save( m2.symp, file = 'm2.symp.Rdata' )
load( 'm2.symp.Rdata' )
```


#### Compare models with & without random nonlinear time effects
Insufficient evidence to support the retention of nonlinear random time coefficients, so drop them from the model
```{r}
anova( m1.symp, m2.symp )
```


### m3.symp: Drop random coefficient for linear time effect

* Results in gain of $df=2$ as random coefficient & correlation between random intercepts & slopes is dropped

```{r}

# m3.symp <- mixed_model( fixed = phq ~ transfer.campus.f*rcs( weeks, 3 ) 
#                 + txcur*rcs( weeks, 3 )
#                 + rcs( procrastct, 3)*rcs( weeks, 3 )
#                 + rcs( bisct, 3)*rcs( weeks, 3 )
#                 + curfin  
#                 + race2 
#                 + male,
#                 random =~ 1 | id,
#                 data = ctsr.use,
#                 family = GLMMadaptive:::negative.binomial()
#                 )
# 
# save( m3.symp, file = 'm3.symp.Rdata' )
load( 'm3.symp.Rdata' )




```


#### Compare random intercept and random intercept + linear time slope models
The random linear time slope effects improve fit, so retain them in the model
```{r}
anova( m2.symp, m3.symp )
```

### m4.symp: Linear effect of procrastination
Simplify model by making the effect of procrastination linear.

```{r}
# 
# m4.symp <- mixed_model( fixed = phq ~ transfer.campus.f*rcs( weeks, 3 )
#                 + txcur*rcs( weeks, 3 )
#                 + procrastct*rcs( weeks, 3 )
#                 + rcs( bisct, 3)*rcs( weeks, 3 )
#                 + curfin
#                 + race2
#                 + male,
#                 random =~ weeks | id,
#                 data = ctsr.use,
#                 family = GLMMadaptive:::negative.binomial()
#                 )
# 
# save( m4.symp, file = 'm4.symp.Rdata' )
load( 'm4.symp.Rdata' )
```

#### Compare models with linear and nonlinear effects of procrastination
No evidence nonlinear effect is needed, so drop it from the model.
```{r}
anova( m4.symp, m2.symp )
```

### m5.symp: Linear effect of procrastination
Simplify model by making the effect of inhibition linear.

```{r}
# 
# m5.symp <- mixed_model( fixed = phq ~ transfer.campus.f*rcs( weeks, 3 )
#                 + txcur*rcs( weeks, 3 )
#                 + procrastct*rcs( weeks, 3 )
#                 + bisct*rcs( weeks, 3 )
#                 + curfin  
#                 + race2 
#                 + male,
#                 random =~ weeks | id,
#                 data = ctsr.use,
#                 family = GLMMadaptive:::negative.binomial()
#                 )
# 
# save( m5.symp, file = 'm5.symp.Rdata' )
load( 'm5.symp.Rdata' )
```

#### Compare models with linear & nonlinear effects of inhibition
No evidence nonlinear effect is needed, so drop it from the model.
```{r}
anova( m5.symp, m4.symp )
```

### m6.symp: Drop covariate*time ineractions
Simplify model by dropping interactions with time for model covariates -- keep exposure*time interaction

```{r}
# 
# m6.symp <- mixed_model( fixed = phq ~ transfer.campus.f*rcs( weeks, 3 )
#                 + txcur
#                 + procrastct
#                 + bisct
#                 + curfin  
#                 + race2 
#                 + male,
#                 random =~ weeks | id,
#                 data = ctsr.use,
#                 family = GLMMadaptive:::negative.binomial()
#                 )
# 
# save( m6.symp, file = 'm6.symp.Rdata' )
load( 'm6.symp.Rdata' )


```


Conduct residual diagnostic analyses to evaluate the tenability of model assumptions. 
```{r}

spline <- rcspline.eval( ctsr.use$weeks, nk = 3 )
ctsr.use1 <- cbind( ctsr.use, spline )
ctsr.use2 <- subset( ctsr.use1, !is.na( ctsr.use1$weeks ) )
ctsr.use3 <- subset( ctsr.use2, !is.na( ctsr.use1$curfin ) )
ctsr.use4 <- subset( ctsr.use3, !is.na( ctsr.use1$procrastct) )
ctsr.use5 <- subset( ctsr.use4, !is.na( ctsr.use1$bisct) )

# m6.symp1 <- mixed_model( fixed = phq ~ transfer.campus.f*weeks + transfer.campus.f*spline
#                 + txcur
#                 + procrastct
#                 + bisct
#                 + curfin
#                 + race2
#                 + sex,
#                 random =~ weeks | id,
#                 data = ctsr.use5,
#                 family = GLMMadaptive:::negative.binomial()
#                 )

save( m6.symp1, file = 'm6.symp1.Rdata' )

# m6.symp1.res <- simulateResiduals( m6.symp1 )
# plot( m6.symp1.res )
# 
# 
# 
# plotResiduals( m6.symp1.res, ctsr.use5$transfer.campus.f )

```


#### Compare models with & without covriate*time interactions
No evidence of covariate by time interactions, so drop them from the model.
```{r}
anova( m6.symp, m5.symp )
```

### m7.symp: Drop nonlinear time effect
Simplify model by dropping nonlinear time effect to gain $df=2$
```{r}

# m7.symp <- mixed_model( fixed = phq ~ transfer.campus.f*weeks
#                 + txcur
#                 + procrastct
#                 + bisct
#                 + curfin  
#                 + race2 
#                 + male,
#                 random =~ weeks | id,
#                 data = ctsr.use,
#                 family = GLMMadaptive:::negative.binomial()
#                 )
# 
# save( m7.symp, file = 'm7.symp.Rdata' )
load( 'm7.symp.Rdata' )

```


#### Compare models with & without covriate*time interactions
No evidence of covariate by time interactions, so drop them from the model.
```{r}
anova( m7.symp, m6.symp )
```

### m8.symp: Exposure by time interaction
Simplify model by dropping effect of student type by time interaction.  Results in gain of $df=4$.
```{r}

# m8.symp <- mixed_model( fixed = phq ~ transfer.campus.f + rcs( weeks, 3 )
#                 + txcur
#                 + procrastct
#                 + bisct
#                 + curfin  
#                 + race2 
#                 + male,
#                 random =~ weeks | id,
#                 data = ctsr.use,
#                 family = GLMMadaptive:::negative.binomial()
#                 )
# 
# save( m8.symp, file = 'm8.symp.Rdata' )
load( 'm8.symp.Rdata' )
```



#### Compare models with & without covriate*time interactions
Compare model with and without student type by time interaction.
```{r}
anova( m8.symp, m6.symp )
```


### m9.symp: Drop expsosure altogether
Simplify model by dropping effect of student type by time interaction.  Results in gain of $df=4$.
```{r}

# m9.symp <- mixed_model( fixed = phq ~ rcs( weeks, 3 )
#                 + txcur
#                 + procrastct
#                 + bisct
#                 + curfin  
#                 + race2 
#                 + male,
#                 random =~ weeks | id,
#                 data = ctsr.use,
#                 family = GLMMadaptive:::negative.binomial()
#                 )

#save( m9.symp, file = 'm9.symp.Rdata' )
load( 'm9.symp.Rdata' )
```


#### Compare models with exposure & time interactions & without exposure altogether
Marginal evidence of an overall effect of student type.
```{r}
anova( m6.symp, m9.symp )
```





```{r}


#m6.symppred <- ggpredict( m6.symp, term=c('weeks [all]','transfer.campus.f'), type = 'fe' ) 

#save( m6.symppred, file = 'm6.symppred.RData'  )


cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

ggsave()
symp.predplot <- ggplot( m6.symppred, aes(x, predicted, colour = group, fill = group ) ) + 
  geom_line( size = 1.25) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high ), alpha = .1, show.legend = F, linetype = 3 ) +
  labs( x = 'Week of the Fall Semester',
    y = 'PHQ-8 Total Depressive Symptom Score',
    colour = 'Student Type',
    title = 'Model-Predicted Mean Depressive Symptom Trajectories',
    subtitle = 'Based on Mixed-Effects Negative Binomial Model',
    caption = 'Adjusts for baseline mental health treatment, race, sex, inhibition, procrastination, & financial comfort') +
  theme( plot.title = element_text( face = 'bold', size = 18, color = 'darkblue', hjust = .5),
         axis.title = element_text( size = 14),
         legend.title = element_text( size = 14, face = 'bold'),
         plot.subtitle = element_text( size = 14, face = 'bold', hjust = .5),
         legend.key.size = unit(1, 'cm'),
         legend.text = element_text( size = 12),
         plot.caption = element_text( size = 12)) +
  scale_fill_manual(values=cbbPalette) +
  scale_color_manual(values = cbbPalette ) +
  geom_vline( xintercept = 0, color = 2 )

symp.predplot  


# ggsave(
#   filename = 'sympplot.tiff',
#   plot = last_plot(),
#   device = 'tiff',
#   dpi = 300,
#   limitsize = TRUE,
#   width = 12,
#   height = 10
# )
```




```{r}

ctsr.use$fycampus <- ifelse( ctsr.use$transfer == 'First-Year' & ctsr.use$campus == 'Off Campus', 1, 0 )


ctsr.use.nofyoff <- subset( ctsr.use, fycampus == 0 )

# m10.symp <- mixed_model( fixed = phq ~ transfer.campus.f*rcs( weeks, 3 )
#                 + txcur
#                 + procrastct
#                 + bisct
#                 + curfin
#                 + race2
#                 + male,
#                 random =~ weeks | id,
#                 data = ctsr.use.nofyoff ,
#                 family = GLMMadaptive:::negative.binomial()
#                 )
# 
# save( m10.symp, file = 'm10.symp.Rdata' )
load( 'm10.symp.Rdata' )
```



```{r}
# m11.symp <- mixed_model( fixed = phq ~ transfer.campus.f + rcs( weeks, 3 )
#                 + txcur
#                 + procrastct
#                 + bisct
#                 + curfin
#                 + race2
#                 + male,
#                 random =~ weeks | id,
#                 data = ctsr.use.nofyoff ,
#                 family = GLMMadaptive:::negative.binomial()
#                 )
# 
# save( m11.symp, file = 'm11.symp.Rdata' )
load( 'm11.symp.Rdata' )


```



```{r}
# m12.symp <- mixed_model( fixed = phq ~ rcs( weeks, 3 )
#                 + txcur
#                 + procrastct
#                 + bisct
#                 + curfin
#                 + race2
#                 + male,
#                 random =~ weeks | id,
#                 data = ctsr.use.nofyoff ,
#                 family = GLMMadaptive:::negative.binomial()
#                 )
# 
# save( m12.symp, file = 'm11.symp.Rdata' )
load( 'm12.symp.Rdata' )
```

# Functioning Analyses


```{r}
cr.vals.role <- cr_setup( ctsr.use$roleemot )
cr.data <- ctsr.use[cr.vals.role$subs, ]
cr.data$roleemot.new <- cr.vals.role$y
cr.data$cohort <- cr.vals.role$cohort
```



```{r}
# m0.role <- mixed_model( fixed = roleemot.new ~ transfer.campus.f*rcs( weeks, 3 )
#                 + txcur*rcs(  weeks, 3 )
#                 + rcs( procrastct, 3)*rcs(  weeks, 3 )
#                 + rcs( bisct, 3)*rcs(  weeks, 3 )
#                 + curfin
#                 + race2
#                 + male
#                 + cohort,
#                 random =~ rcs( weeks, 3 ) | id,
#                 data = cr.data,
#                 family = binomial()
#                 )
# 
# save( m0.role, file = 'm0.role.Rdata' )
load( 'm0.role.Rdata' )
```




```{r}
m1.role <- mixed_model( fixed = roleemot.new ~ transfer.campus.f*rcs( weeks, 3 )
                + txcur*rcs(  weeks, 3 )
                + rcs( procrastct, 3)*rcs(  weeks, 3 )
                + rcs( bisct, 3)*rcs(  weeks, 3 )
                + curfin
                + race2
                + male
                + cohort,
                random =~ weeks | id,
                data = cr.data,
                family = binomial()
                )

save( m1.role, file = 'm1.role.Rdata' )
load( 'm1.role.Rdata' )
```



```{r}
( lrt.m1role.m0role <- anova( m1.role, m0.role ) )
```

```{r}
m2.role <- mixed_model( fixed = roleemot.new ~ transfer.campus.f*rcs( weeks, 3 )
                + txcur*rcs(  weeks, 3 )
                + rcs( procrastct, 3)*rcs(  weeks, 3 )
                + rcs( bisct, 3)*rcs(  weeks, 3 )
                + curfin
                + race2
                + male
                + cohort,
                random =~ 1 | id,
                data = cr.data,
                family = binomial()
                )

save( m2.role, file = 'm2.role.Rdata' )
load( 'm2.role.Rdata' )
```


```{r}
( lrt.m2role.m1role <- anova( m2.role, m1.role ) )
```




```{r}
m3.role <- mixed_model( fixed = roleemot.new ~ transfer.campus.f*rcs( weeks, 3 )
                + txcur*rcs(  weeks, 3 )
                + procrastct*rcs(  weeks, 3 )
                + rcs( bisct, 3)*rcs(  weeks, 3 )
                + curfin
                + race2
                + male
                + cohort,
                random =~ weeks | id,
                data = cr.data,
                family = binomial()
                )

save( m3.role, file = 'm3.role.Rdata' )
load( 'm3.role.Rdata' )
```



```{r}
( lrt.m3role.m1role <- anova( m3.role, m1.role ) )
```

```{r}
m4.role <- mixed_model( fixed = roleemot.new ~ transfer.campus.f*rcs( weeks, 3 )
                + txcur*rcs(  weeks, 3 )
                + rcs( procrastct, 3)*rcs(  weeks, 3 )
                + bisct*rcs(  weeks, 3 )
                + curfin
                + race2
                + male
                + cohort,
                random =~ weeks | id,
                data = cr.data,
                family = binomial()
                )

save( m4.role, file = 'm4.role.Rdata' )
load( 'm4.role.Rdata' )
```


```{r}
( lrt.m4role.m1role <- anova( m4.role, m1.role ) )
```




```{r}
m5.role <- mixed_model( fixed = roleemot.new ~ transfer.campus.f*rcs( weeks, 3 )
                + txcur 
                + rcs( procrastct, 3) 
                + bisct 
                + curfin
                + race2
                + male
                + cohort,
                random =~ weeks | id,
                data = cr.data,
                family = binomial()
                )

save( m5.role, file = 'm5.role.Rdata' )
load( 'm5.role.Rdata' )
```


```{r}
( lrt.m5ole.m4role <- anova( m5.role, m4.role ) )
```


```{r}
m6.role <- mixed_model( fixed = roleemot.new ~ transfer.campus.f*weeks
                + txcur 
                + rcs( procrastct, 3) 
                + bisct 
                + curfin
                + race2
                + male
                + cohort,
                random =~ weeks | id,
                data = cr.data,
                family = binomial()
                )

save( m6.role, file = 'm6.role.Rdata' )
load( 'm6.role.Rdata' )
```



```{r}
( lrt.m6ole.m5role <- anova( m6.role, m5.role ) )
```




```{r}

m7.role <- mixed_model( fixed = roleemot.new ~ transfer.campus.f + rcs( weeks, 3 ) 
                + txcur 
                + rcs( procrastct, 3) 
                + bisct 
                + curfin
                + race2
                + male
                + cohort,
                random =~ weeks | id,
                data = cr.data,
                family = binomial()
                )

save( m7.role, file = 'm7.role.Rdata' )
load( 'm7.role.Rdata' )


weeks2 <- data.frame( rcspline.eval( cr.data$weeks, nk = 3 ) )


```



```{r}
( lrt.m7ole.m5role <- anova( m7.role, m5.role ) )
```

```{r}
m8.role <- mixed_model( fixed = roleemot.new ~  weeks
                + txcur 
                + rcs( procrastct, 3) 
                + bisct 
                + curfin
                + race2
                + male
                + cohort,
                random =~ weeks | id,
                data = cr.data,
                family = binomial()
                )

save( m8.role, file = 'm8.role.Rdata' )
load( 'm8.role.Rdata' )
```


```{r}
( lrt.m8ole.m6role <- anova( m8.role, m6.role ) )
```





```{r}
m7.role.pred  <- ggpredict( m7.role, term=c('weeks [all]','transfer.campus.f' ) ) 
```

```{r}
require( ordinal )


m7a.role <- clmm( ordered( roleemot ) ~ transfer.campus.f + rcs( weeks, 3 ) 
                + txcur 
                + rcs( procrastct, 3) 
                + bisct 
                + curfin
                + race2
                + male
                + cohort
                + ( weeks | id ),
                data = ctsr.use,
                nAGQ = 1
                )

save( m7a.role, file = 'm7a.role.Rdata' )
load( 'm7a.role.Rdata' )

```

